\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/ms.tex
update tables

\paragraph{Manually curated questions}
Manually curated questions were sourced from various sources, including university exams, textbooks, and question banks. \Cref{tab:manually_sources} provides an overview of the sources of the manually curated questions.
\begin{table}
\input{sections/manually_sources_table.tex}
\label{tab:manually_sources}
\end{table}

\paragraph{Semi-programatically generated questions}

\begin{table}
\input{sections/semi_programatically_sources_table.tex}
\end{table}

>>>>

\paragraph{Manually curated questions}
Manually curated questions were sourced from various sources, including university exams, textbooks, and question banks. \Cref{tab:manually_sources} provides an overview of the sources of the manually curated questions.
\begin{table}[h]
\caption{\textbf{Sources of manually curated questions.} The table shows the sources and a brief description  as well as the number of the manually curated questions.}
\input{sections/manually_sources_table.tex}
\label{tab:manually_sources}
\end{table}

\paragraph{Semi-programatically generated questions}
In addition to the manually curated questions, we also generated questions programmatically. An overview of the sources of the semi-programatically generated questions is provided in \Cref{tab:semi_programatically_sources}.

\begin{table}[h]
\caption{\textbf{Sources of semi-programatically generated questions.} The table shows the sources and a brief description as well as the number of the semi-programatically generated questions.}
\input{sections/semi_programatically_sources_table.tex}
\label{tab:semi_programatically_sources}
\end{table}
